

% \section{Related Work}

\noindent \textbf{Usecases}

~\cite{cartas_reality_2019} questions the need for edge computing for ML inference, because of the decreasing inference latency and costs, and network latency becomes the primary bottleneck.

Berkeley view~\cite{jonas2017occupy, jonas_cloud_2019}

Interactive applications---RunBox ~\cite{glikson_runbox_2019}.

Data analytics with ServerMix~\cite{garcia-lopez_servermix_2019}

ExCamera

PyWren

Serverless analytics with Flint wtf

From laptop to lambda ~\cite{fouladi_laptop_2019}

Monolithic to serverless with Ripple~\cite{joyner_ripple_2020}

HPC~\cite{mocskos_faaster_2018}

SPEC group report~\cite{van_eyk_spec_2017}

\noindent \textbf{cold start problem}

~\cite{lin_mitigating_2019} is a project report that uses ML inference, webserver workloads as we are. Knative platform. Maintain a pool of warm containers. No real policy though.

HyperFaas claims to address cold start problem? ~\cite{zhang_hyperfaas_2019}. 

\noindent \textbf{Frameworks}

Cirrus~\cite{carreira_cirrus_2019} does end to end ML model training, hyperparam tuning on a new serveless framework. Not inference though?

SAND~\cite{akkus_sand_2018} is based on openwhisk, but focused more on the inter function messaging?

Wukong~\cite{carver_search_2019} has an interesting DAG scheduling solution---decentralized scheduling. Evalutes on numerical computing problems and compares with Dask (Python).

SPOCK~\cite{gunasekaran_spock_2019} combines VMs and serverless functions. 

Named functions as a service~\cite{krol_nfaas_2017}---uses unikernels!!
More work along similar lines~\cite{lin_computation_2019,mtibaa_towards_2018,xylomenos_named_2019,krol_computation_2018}


Peeking behind the curtains

SOCK~\cite{oakes_sock_2018}

OpenLambda~\cite{hendrickson2016serverless}

GrandSlam ~\cite{kannan_grandslam_2019} ~\cite{} tries to provide SLA guarantees for microservices.

Performance comparison by Geoffrey~\cite{lee_evalution_2018}


\noindent \textbf{Resource management}

Auction based function placement in serverless~\cite{bermbach_towards_2019}.

Checkpointing and migration with CRIU for IoT devices in~\cite{karhula_checkpointing_2019}. What's the motivation with stateless functions? Nothing---they focus on stateful functions.


``Living on the edge''~\cite{kulkarni_living_2019} explores transaction support and fault tolerance for stream processing. 


Data management (really caching?) with the Locus shuffling system~\cite{pu_shuffling_2019}. 


Caching strategies for data in~\cite{ghosh_caching_2019}

More storage optimizations?~\cite{zhang_narrowing_2019}

\noindent \textbf{Formal }

~\cite{hall_execution_2019} provides an architecture with WASM on the edge.

~\cite{riis_nielson_no_2019} provides a serverless kernel calculus combining lambda calculus for computation and pi-calculus for communication.





%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:
